### 2020-07-23 paper/main.tex
Add jewel picture

\usepackage{appendix}
\usepackage{todonotes}
\usepackage{wrapfig}

\usepackage{tikz}
\tikzset{%
    simplegraph/.style={every node/.style={draw,circle, inner sep=0pt, minimum size=6mm}},
}

@@

@@

@@

\begin{wrapfigure}{r}{0.35\textwidth}
	\centering\begin{tikzpicture}[scale=0.7,simplegraph]
	\node(a) at (0,0) {a};
	\node(b1) at (-2,-6) {$b_1$};
	\node(b2) at (0,-4.268) {$b_2$};
	\node(b3) at (2,-6) {$b_3$};

@@

It is easy to see that every graph containing a pyramid contains an odd hole.

\TODO{On recognition of pyramids.}

>>>>

\usepackage{appendix}
\usepackage{todonotes}
\usepackage{wrapfig}
\usepackage{intcalc}

\usepackage{tikz}
\tikzset{%
    simplegraph/.style={every node/.style={draw,circle, inner sep=0pt, minimum size=6mm}},
}
\usetikzlibrary{snakes}
\usetikzlibrary{shapes.geometric}

@@

\paragraph{Editorial notes}
By solid lines we will mark edges, by dashed lines we will mark nonedges, when significant. Sometimes nonedges will not be marked in order not to clutter the image.
\todo{Where should we put it?}

@@

\paragraph{Pyramids}

@@

\begin{wrapfigure}[12]{r}{0.35\textwidth}
	\centering\begin{tikzpicture}[scale=0.7,simplegraph]
	\node(a) at (0,0) {a};
	\node(b1) at (-2,-6) {$b_1$};
	\node(b2) at (0,-4.268) {$b_2$};
	\node(b3) at (2,-6) {$b_3$};

@@

It is easy to see that every graph containing a pyramid contains an odd hole -- at least two of the paths $P_1$, $P_2$, $P_3$ will have the same parity.

\TODO{On recognition of pyramids. Lemma 2.1 from the paper.}

\paragraph{Jewels}

\begin{wrapfigure}[12]{r}{0.35\textwidth}
	\centering\begin{tikzpicture}[scale=0.7,simplegraph]
	\def\ngon{5}
	\node[regular polygon,regular polygon sides=\ngon,minimum size=3cm, draw=none] (p) {};
	\foreach\x in {1,...,\ngon}{\node[] (p\x) at (p.corner \x){$v_\the\numexpr\intcalcMod{\x+3}{5}+1$};}
	%p1 - v5, p2 - v1 ...
	\draw (p1) to (p2);
	\draw (p2) to (p3);
	\draw (p3) to (p4);
	\draw (p4) to (p5);
	\draw (p1) to (p5);

  \draw[dashed] (p2) to (p5);
  \draw[dashed] (p2) to (p4);
	\draw[dashed] (p3) to (p5);

	\tikzset{decoration={snake,amplitude=.6mm,segment length=6mm,
                       post length=0mm,pre length=0mm}}
	\draw[decorate] (p2) to [out=-100, in=180] (0, -5) to [out=0, in=-80] (p5);
	\node[draw=none] at (0, -4.7) {$P$};
\end{tikzpicture}
\caption{An example of a jewel.}
\end{wrapfigure}

Five nodes $v_1, \ldots, v_5$ and a path $P$ is a \emph{jewel} iff:

\begin{itemize}
	\item $v_1, \ldots, v_5$ are distinct nodes.
	\item $v_1v_2, v_2v_3, v_3v_4, v_4v_5, v_5v_1$ are edges.
	\item $v_1v_3, v_2v_4, v_1,v_4$ are nonedges.
	\item $P$ is a path between $v_1$ and $v_4$, such that $v_2, v_3, v_5$ have no neighbors in its inside.
\end{itemize}
